Pillar 1 - Sequential Pattern Mining

### 2019-03-22 Pillar 1 - Sequential Pattern Mining.Rmd
minor change

AR with not taken on lhs is not useful.

@@

  # lhs: past courses and courses not taken yet, rhs: current courses
  mutate(
    lhs = list(course_past, course_not_yet) %>% pmap(union),
    rhs = course_current
    ) %>%

  select(lhs, rhs) # for memory requirement
```

@@

```{r rules_rules}
rules_clean <- rules_clean %>% mutate(rules_rules = rules %>% map(edit_rules))
```

>>>>

@@

  # lhs: past courses and courses not taken yet, rhs: current courses
  mutate(
    lhs = list(course_past, course_not_yet) %>% pmap(union),
    rhs = course_current
    )
```

```{r}
save(d_transcript_cum, file = "output/d_transcript_cum.RDATA")
```

@@

```{r rules_rules}
rules_clean <- rules_clean %>% mutate(rules_rules = rules %>% map(edit_rules)) %>% select(-rules)
```
